---
title: "Regression Machine Learning"
output:
  github_document: default
---
## Introduction

```{r, message=FALSE}
library(PerformanceAnalytics)
library(ggplot2)
library(Metrics)
library(tsensembler)

#reading file
beijing.pm <- read.csv("~/Desktop/learning/ML/PRSA_data_2010.1.1-2014.12.31.csv", stringsAsFactors = FALSE)

#overview of the data
dim(beijing.pm)
head(beijing.pm)
tail(beijing.pm)
str(beijing.pm)
summary(beijing.pm)

#missing values of the data
sum(is.na(beijing.pm))

(2067/43924) * 100
```

The missing value in the dataset is remove. Since missing value only represents 4.705% of the data. Thus, it does not have the huge impact on the dataset once it is removed
```{r}

beijing.pm.omit <- na.omit(beijing.pm)

sum(is.na(beijing.pm.omit))

summary(beijing.pm.omit)
```

## Exploratory data analysis
```{r, warning=FALSE, message=FALSE}
#correlation
#get the desire variables

beijing.pm.corr <- beijing.pm.omit[,c(6,7,8,9)]

chart.Correlation(beijing.pm.corr, histogram=TRUE, method = "pearson")
```

The correlation shows that PM2.5 is highly correlated with Dew Point, Temperature and Pressure.

### Preparing for training and test set
```{r}
#shuffle dataset and create train and test set
set.seed(1234567)
n <- nrow(beijing.pm.corr)
shuffled <- beijing.pm.corr[sample(n),]

train <- shuffled[1:round(0.7 * n),]
test <- shuffled[(round(0.7 * n) + 1):n,]

summary(train)
summary(test)
```

##Trainning the model

```{r}
model.train <- lm(pm2.5 ~ ., data = train)
round(model.train$coefficients,3)
```

Checking confidence interval
```{r}
round(confint(model.train, level = 0.95), 3)
```

Check the model performance
```{r}
summary(model.train)
```

```{r}
plot(model.train)
```

Assessing test set performance
```{r}
pred <- predict(model.train, test)
head(pred)
```

Plotting of train and test data against actural performance
```{r}
train$pred <- predict(model.train)
test$pred <- predict(model.train, test)

plot.train <- ggplot(train, aes(x = pred, y = pm2.5)) +
  geom_point() +
  geom_abline(color = "red")

plot.test <- ggplot(test, aes(x = pred, y = pm2.5)) +
  geom_point() +
  geom_abline(color = "red")

plot.train
plot.test
```

```{r}
# Evaluate the rmse on both training and test data and print them
(rmse_train <- rmse(train$pred, train$pm2.5))
(rmse_test <- rmse(test$pred, test$pm2.5))


# Evaluate the r-squared on both training and test data.and print them
train.rss <- sum((train$pred - train$pm2.5) ^ 2)
train.tss <- sum((train$pm2.5 - mean(train$pm2.5)) ^ 2)
(rsq <- 1 - train.rss/train.tss)

test.rss <- sum((test$pred - test$pm2.5) ^ 2)
test.tss <- sum((test$pm2.5 - mean(test$pm2.5)) ^ 2)
(rsq <- 1 - test.rss/test.tss)

```